%------------------------------------------------------------------------------
\chapter*{Make a flying start in your project}
%------------------------------------------------------------------------------
\section*{Goal}
%------------------------------------------------------------------------------
When a product owner invites to tender for a (software) construction contract,
it takes typically too long to understand the scope of the project to make a
sufficiently accurate estimation of effort. Often, the first phase of 
installation, building and setting up an evaluation environment takes months.
Only then the second phase of understanding the complete scope can start.
With `flying start' we intend to reduce the first phase to less than 10 minutes.

%------------------------------------------------------------------------------
\section*{Function description}
%------------------------------------------------------------------------------
'Flying Start' is a research project and the last major hurdle is the
expression of make/build relations in the native language, being C++. Currently,
OS specific scripts are used for building software and documentation, and it is
desired to replace this by a pure C++ solution (no make, cmake, etc.) 
Overcoming this hurdle enables true multiplatform support.
This challenging cppmake sub-project is to be based on dependency graphs.
You'll be working in a environment of C++, git, LaTeX, UML and scrum, with a 
focus on platform independence and IDE independence.

%------------------------------------------------------------------------------
\section*{cppmake details}
%------------------------------------------------------------------------------
For details, please create an account on \url{github.com/join}, and
select "Clone or download" for repository 
\url{github.com/kubicas/flying_start_internship07}, followed by "Download ZIP".
Unzip this repository, including its directory structure. Assure there are no
spaces in the path and execute 
!.../procts/flying_start/winx86r/internship07.exe! on a Windows machine, which will 
download and build the whole environment you'll be working in. Start reading 
the automatically built
!.../procts/internship07/tgt/doc/assignment.pdf!.

%------------------------------------------------------------------------------
\section*{Expectations}
%------------------------------------------------------------------------------
\begin{itemize}
\item Knowledge of modern C++ and interest to extend this knowledge
\item Knowledge of LaTeX or interest in learning LaTeX
\item Interest in multi-platform C++ solutions
\item Interest in the C++ standard template library
\item Being able to work independently
\item Having downloaded and read above mentioned !assignment.pdf! before applying
\end{itemize}

%------------------------------------------------------------------------------
\section*{Company profile}
%------------------------------------------------------------------------------

ALTEN is the consulting and engineering organization working in various (niche) 
markets for the high tech sector and ICT. The high-tech sector consists of 
several closely interconnected manufacturing industries, such as the machine 
and systems industries, automotive and aerospace. Knowledge in the field of 
technology plays an important role, th\'{e} central pillar within ALTEN.